### 2021-02-16 ch06_paper_gpp/paper_gpp.tex
Added further code and figures to chapter 06

\begin{figure}[t]
  \centering
  \includegraphics[width=\LargeFigureWidth{}]{
    ch06_paper_gpp/figs/schematic_steps.pdf}
  \caption{Schematic illustration of our two-step approach. In step 1 an
    emergent constraint by \textcite{Wenzel2016} is used to constrain the
    global mean fractional change in \acf{GPP} over the 21st century.
    Moreover, this constraint is used to rescale two different gridded target
    variables: absolute \acs{GPP} at the end of the \nth{21} century and
    fractional \acs{GPP} change over the \nth{21} century. In step 2, a
    \acl{ML} model is used to constrain these two target variables (step 2a:
    absolute \acs{GPP}; step 2b: fractional \acs{GPP} change) in two
    independent approaches. \AdaptedFrom{Schlund2020a}.}
  \label{fig:06:schematic_steps}
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=\LargerFigureWidth{}]{
    ch06_paper_gpp/figs/mlr_concept.pdf}
  \caption{Schematic illustration of our \acf{ML} approach to constrain
    projected absolute \acf{GPP} in step 2a. (a) In the training phase of the
    algorithm, the model is fitted to the training data interpolating the
    empirical (non-linear) relationship between two process-oriented
    diagnostics of the past climate $\left\{ x^{(1)}, x^{(2)} \right\}$ and
    (rescaled) future \acs{GPP} (gray surface). The points show the training
    points for the supervised \acs{ML} algorithm, each of them representing a
    single grid cell/month of a single climate model (the different colors
    correspond to different climate models). (b) In the prediction phase,
    observation-based values of the diagnostic (black points) are fed into the
    trained \acs{ML} model to constrain \acs{GPP} for every grid cell/month to
    a value which best agrees with the observations. (c) For an independent
    validation of our method, we use an out-of-sample testing setup based on a
    leave-one-model-out \acl{CV} approach (see
    \cref{subsec:02:model_weighting} for details). The schematic illustration
    of step 2b differs only in the target variable used (fractional \acs{GPP}
    change instead of absolute \acs{GPP}). \AdaptedFrom{Schlund2020a}.}
  \label{fig:06:mlr_concept}
\end{figure}

@@

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=\LargeFigureWidth{}]{
    ch06_paper_gpp/figs/schematic_steps.pdf}
  \caption{Schematic illustration of our two-step approach. In step 1 an
    emergent constraint by \textcite{Wenzel2016} is used to constrain the
    global mean fractional change in \acf{GPP} over the 21st century.
    Moreover, this constraint is used to rescale two different gridded target
    variables: absolute \acs{GPP} at the end of the \nth{21} century and
    fractional \acs{GPP} change over the \nth{21} century. In step 2, a
    \acl{ML} model is used to constrain these two target variables (step 2a:
    absolute \acs{GPP}; step 2b: fractional \acs{GPP} change) in two
    independent approaches. \AdaptedFrom{Schlund2020}.}
  \label{fig:06:schematic_steps}
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=\LargerFigureWidth{}]{
    ch06_paper_gpp/figs/mlr_concept.pdf}
  \caption{Schematic illustration of our \acf{ML} approach to constrain
    projected absolute \acf{GPP} in step 2a. (a) In the training phase of the
    algorithm, the model is fitted to the training data interpolating the
    empirical (non-linear) relationship between two process-oriented
    diagnostics of the past climate $\left\{ x^{(1)}, x^{(2)} \right\}$ and
    (rescaled) future \acs{GPP} (gray surface). The points show the training
    points for the supervised \acs{ML} algorithm, each of them representing a
    single grid cell/month of a single climate model (the different colors
    correspond to different climate models). (b) In the prediction phase,
    observation-based values of the diagnostic (black points) are fed into the
    trained \acs{ML} model to constrain \acs{GPP} for every grid cell/month to
    a value which best agrees with the observations. (c) For an independent
    validation of our method, we use an out-of-sample testing setup based on a
    leave-one-model-out \acl{CV} approach (see
    \cref{subsec:02:model_weighting} for details). The schematic illustration
    of step 2b differs only in the target variable used (fractional \acs{GPP}
    change instead of absolute \acs{GPP}). \AdaptedFrom{Schlund2020}.}
  \label{fig:06:mlr_concept}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \raisebox{5.5mm}{\includegraphics[width=\columnwidth]{
      ch06_paper_gpp/figs/step2a_rmse.pdf}}
    \caption{}
    \label{fig:06:step2a_ml_inference:a}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch06_paper_gpp/figs/step2a_global_feature_importance.pdf}
    \caption{}
    \label{fig:06:step2a_ml_inference:b}
  \end{subfigure}
  \caption{(a) Box plot of the \acf{RMSEP} distributions for six different
    statistical models used to predict future absolute \acf{GPP} in step 2a
    using a leave-one-model-out \acl{CV} approach. The distribution for each
    statistical model contains seven elements (black points; one for each
    climate model used as truth) and is represented in the following way: The
    lower and upper limit of the blue boxes correspond to the $25 \unit{\%}$
    and $75 \unit{\%}$ quantiles, respectively. The central line in the box
    shows the median and the black \enquote{x} shows the mean of the
    distribution. The whiskers outside the box represent the range of the
    distribution. Compared to the \acs{CMIP}5 \acf{MMM} and its corresponding
    rescaled version (r\acs{MMM}), the prediction uncertainty measured by the
    mean \acs{RMSEP} is significantly reduced by up to $48 \unit{\%}$ and $39
    \unit{\%}$, respectively, when using other statistical models. Moreover,
    the non-linear \acf{GBRT} models can slightly reduce the mean \acs{RMSEP}
    compared to the linear \acf{LASSO} models by about $2 \unit{\%}$ for
    \acs{GBRT}-1D (using historical \acs{GPP} as single predictor) and $3
    \unit{\%}$ for the full \acs{GBRT} model (using all predictors). (b)
    Relative global feature importance for the different predictors used in
    the \acs{GBRT} model to predict future absolute \acs{GPP} (step 2a). The
    red bars correspond to positive Pearson correlation coefficients between
    all predictors and the target variable. Due to its strong positive linear
    relationship with the future \acs{GPP}, the historical \acs{GPP} is by far
    the most important predictor in the model. A local feature importance map
    using \acf{LIME} is not shown here because \acs{GPP} is the dominant
    predictor for all grid cells. \AdaptedFrom{Schlund2020}.}
  \label{fig:06:step2a_ml_inference}
\end{figure}

### 2021-02-16 end_acronyms/acronyms.tex
Added subsection on calculation of CRE feedback parameters
Added contributions to ESMValCore to chapter 03
Cleaned code
Added figures for ESMValTool contributions (chapter 3)
Finished chapter 3
Cleaned tex files and added text to chapter 4
Added text and figures to section 4.1
Added tables for chapter 05
Added first parts of section 5.2
Finished section 5.2
Added introduction of chapter 06 and fixed some acronyms
Added first figures for chapter 6
Added further code and figures to chapter 06

\begingroup
\setstretch{0.5}
\begin{acronym}
  \acro{AerChemMIP}{Aerosol Chemistry Model Intercomparison Project}
  \acro{AOGCM}{Atmosphere-Ocean General Circulation Model}
  \acro{AR}{Assessment Report}
  \acro{C4MIP}{Coupled Climate-Carbon Cycle Model Intercomparison Project}
  \acro{CESM}{Community Earth System Model}
  \acro{CMIP}{Coupled Model Intercomparison Project}
  \acro{CH4}[CH\textsubscript{4}]{methane}
  \acro{CMOR}{Climate Model Output Rewriter}
  \acro{CO}{carbon monoxide}
  \acro{CO2}[CO\textsubscript{2}]{carbon dioxide}
  \acro{CV}{cross-validation}
  \acro{DECK}{Diagnostic, Evaluation, and Characterisation of Klima}
  \acro{DLR}{%
    Deutsches Zentrum für Luft- und Raumfahrt (German Aerospace Center)}
  \acro{ECS}{Effective Climate Sensitivity}
  \acro{ENSO}{El Niño-Southern Oscillation}
  \acro{ESGF}{Earth System Grid Federation}
  \acro{ESM}{Earth System Model}
  \acro{ESMValCore}{core functionalities of the ESMValTool}
  \acro{ESMValTool}{Earth System Model Evaluation Tool}
  \acro{GHG}{Greenhouse Gas}
  \acro{GPP}{Gross Primary Productivity}
  \acro{GSAT}{global mean near-surface air temperature}
  \acro{GtC}{gigatonnes of carbon}
  \acro{I/O}{Input/Output}
  \acro{IAM}{Integrated Assessment Models}
  \acro{IPA}{%
    Institut für Physik der Atmosphäre (Institute of Atmospheric Physics)}
  \acro{IPCC}{Intergovernmental Panel on Climate Change}
  \acro{LongRunMIP}{Long Run Model Intercomparison Project}
  \acro{MDER}{Multiple Diagnostic Ensemble Regression}
  \acro{MIP}{Model Intercomparison Project}
  \acro{ML}{Machine Learning}
  \acro{MMM}{multi-model mean}
  \acro{NAO}{North Atlantic Oscillation}
  \acro{NCAR}{National Center for Atmospheric Research}
  \acro{netCDF}{Network Common Data Form}
  \acro{PDF}{probability density function}
  \acro{ppm}{parts per million}
  \acro{RCP}{Representative Concentration Pathway}
  \acro{RMSE}{root-mean-square error}
  \acro{ScenarioMIP}{Scenario Model Intercomparison Project}
  \acro{SSP}{Shared Socioeconomic Pathway}
  \acro{TCR}{Transient Climate Response}
  \acro{TOA}{top of the atmosphere}
  \acro{WCRP}{World Climate Research Programme}
  \acro{WGCM}{Working Group on Coupled Modelling}
\end{acronym}
\endgroup

>>>>

\begingroup
\setstretch{0.5}
\begin{acronym}
  \acro{AerChemMIP}{Aerosol Chemistry Model Intercomparison Project}
  \acro{AOGCM}{atmosphere-ocean general circulation model}
  \acro{AR}{Assessment Report}
  \acro{C4MIP}{Coupled Climate-Carbon Cycle Model Intercomparison Project}
  \acro{CESM}{Community Earth System Model}
  \acro{CFMIP}{Cloud Feedback Model Intercomparison Project}
  \acro{CMIP}{Coupled Model Intercomparison Project}
  \acro{CH4}[CH\textsubscript{4}]{methane}
  \acro{CMOR}{Climate Model Output Rewriter}
  \acro{CO}{carbon monoxide}
  \acro{CO2}[CO\textsubscript{2}]{carbon dioxide}
  \acro{CRE}{cloud radiative effect}
  \acro{CV}{cross-validation}
  \acro{DECK}{Diagnostic, Evaluation, and Characterisation of Klima}
  \acro{DJF}{December-January-February}
  \acro{DLR}{%
    Deutsches Zentrum für Luft- und Raumfahrt (German Aerospace Center)}
  \acro{ECS}{effective climate sensitivity}
  \acro{ENSO}{El Niño-Southern Oscillation}
  \acro{ESGF}{Earth System Grid Federation}
  \acro{ESM}{Earth system model}
  \acro{ESMValCore}{core functionalities of the ESMValTool}
  \acro{ESMValTool}{Earth System Model Evaluation Tool}
  \acro{GBRT}{gradient boosted regression tree}
  \acro{GHG}{greenhouse gas}
  \acro{GPP}{gross primary production}
  \acro{GSAT}{global mean near-surface air temperature}
  \acro{GtC}{gigatonnes of carbon}
  \acro{IAM}{integrated assessment model}
  \acro{IPA}{%
    Institut für Physik der Atmosphäre (Institute of Atmospheric Physics)}
  \acro{IPCC}{Intergovernmental Panel on Climate Change}
  \acro{ITCZ}{Intertropical Convergence Zone}
  \acro{JJA}{June-July-August}
  \acro{LASSO}{least absolute shrinkage and selection operator}
  \acro{LIME}{local interpretable model-agnostic explanations}
  \acro{LongRunMIP}{Long Run Model Intercomparison Project}
  \acro{LTMI}{lower-tropospheric mixing index}
  \acro{MBLC}{marine boundary layer cloud}
  \acro{MDER}{multiple diagnostic ensemble regression}
  \acro{MIP}{Model Intercomparison Project}
  \acro{ML}{machine learning}
  \acro{MMM}{multi-model mean}
  \acro{NAO}{North Atlantic Oscillation}
  \acro{NCAR}{National Center for Atmospheric Research}
  \acro{netCDF}{Network Common Data Form}
  \acro{PDF}{probability density function}
  \acro{ppm}{parts per million}
  \acro{RCP}{Representative Concentration Pathway}
  \acro{RMSE}{root-mean-square error}
  \acro{RMSEP}{root-mean-square error of prediction}
  \acro{ScenarioMIP}{Scenario Model Intercomparison Project}
  \acro{SSP}{Shared Socioeconomic Pathway}
  \acro{SST}{sea surface temperature}
  \acro{TCR}{transient climate response}
  \acro{TLC}{tropical low-level cloud}
  \acro{TOA}{top of the atmosphere}
  \acro{WCRP}{World Climate Research Programme}
  \acro{WGCM}{Working Group on Coupled Modelling}
\end{acronym}
\endgroup
